Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-09 papers/integration/omm_integ.tex
Nearly done with Reviewer 1's comments on the RESULTS section

Figs.~\ref{errorsurface}(a)--(d) show the same percentage errors for
TModel4 as Fig.~\ref{errorsurfaceTM3} shows for TModel3.  First of
all, note that the error magnitudes are much smaller. The mean errors
are smaller for every axis. The largest errors produced by the model
are approximately 15\%, which are within the boundaries of what some
authors have suggested would be regarded as an accurate
saccade \citep{mcpeek_saccade_2002,mcpeek_incomplete_2006}.  The
magnitude of the largest error vector is approximately 1.5\dg.

@@

We investigated the behaviour of the model for saccade sequences.  In
one experiment, we illuminated a fixation cross from 0~s until 0.4~s,
followed by a target at (0,-10\dg) from 0.4~s until 0.8~s. Finally,
the fixation was again shown from 0.8~s until the end of the
simulation at 2~s. This induced a saccade to a 10\dg~eccentricity,
followed by a return saccade back to the null point. We noticed some
irregularities in the return saccades, which though surprisingly
accurate, had a significant overshoot.  More perplexingly, if the
target was switched repeatedly between 0\dg~and 10\dg, second and
subsequent \e{outward} saccades also showed this overshoot. We found
that the cause of these irregularties was the lack (in `TModel4') of
any mechanism to reset the tonic neurons in the SBG after the first
saccade. This resulted in TN activity in the left channel \e{and also}
in the right channel. Interestingly, this ensured that, at least for a
few, consecutive out-and-return saccades, the saccade accuracy was
relatively good, with trajectories resembling experimental data
(\cite{bahill_trajectories_1979}, p.~6). % Poss. figure.
Nevertheless, the lack of a reset of TN activity was an oversight, and
is indeed proposed and included in the connectivity of the
\cite{gancarz_neural_1998} model. We implemented this feature by adding an
additional inhibitory input to the `integrator' component of TModel4,
driven by the contralateral EBN population, naming the new model
`TModel5'.  Now, when the eye is directed towards an eccentric target
which is then exchanged with a target at the null point, the EBN
activity toward the null point will tend to extinguish the TN activity
which was holding the eye at the eccentric position.  We verified that
none of the single saccade results were affected by this modification.
% This doesn't account for *all* cases where you'd want to remove the
% TN activity. Imagine a saccade purely UP then a saccade to a
% location purely RIGHT. You'd need to remove the TN activity on the
% UP channel, but you'd not be inducing any DOWN with the new target.

>>>>

Figs.~\ref{errorsurface}(a)--(d) show the \rvw{percentage errors for
TModel4}.  First of
all, note that the error magnitudes are much smaller. The mean errors
are smaller for every axis. The largest errors produced by the model
are approximately 15\%, which are within the boundaries of what some
authors have suggested would be regarded as an accurate
saccade \citep{mcpeek_saccade_2002,mcpeek_incomplete_2006}.  The
magnitude of the largest error vector is approximately 1.5\dg.

@@

We investigated the behaviour of the model for saccade sequences.  In
one experiment, we illuminated a fixation cross from 0~s until 0.4~s,
followed by a target at (0,-10\dg) from 0.4~s until 0.8~s. Finally,
the fixation was again shown from 0.8~s until the end of the
simulation at 2~s. This induced a saccade to a 10\dg~eccentricity,
followed by a return saccade back to the null point. We noticed some
irregularities in the return saccades, which \rvw{were
accurate}, but had a significant overshoot.  More perplexingly, if the
target was switched repeatedly between 0\dg~and 10\dg, second and
subsequent \e{outward} saccades also showed this overshoot. We found
that the cause of these irregularties was the lack (in `TModel4') of
any mechanism to reset the tonic neurons in the SBG after the first
saccade. This resulted in TN activity in the left channel \e{and also}
in the right channel. Interestingly, this ensured that, at least for a
few, consecutive out-and-return saccades, the saccade accuracy was
accidently relatively good, with trajectories resembling experimental data
(\cite{bahill_trajectories_1979}, p.~6). \rvw{Had the return accuracy not
been so accurate, we may have noticed the lack of a tonic neuron reset
mechanism and corrected this oversight earlier.} Such a mechanism
is indeed proposed and included in the connectivity of the
\cite{gancarz_neural_1998} model. We implemented this feature by adding an
additional inhibitory input to the `integrator' component of TModel4,
driven by the contralateral EBN population, naming the new model
`TModel5'.  Now, when the eye is directed towards an eccentric target
which is then exchanged with a target at the null point, the EBN
activity toward the null point will tend to extinguish the TN activity
which was holding the eye at the eccentric position.  We verified that
none of the single saccade results were affected by this modification.
% This doesn't account for *all* cases where you'd want to remove the
% TN activity. Imagine a saccade purely UP then a saccade to a
% location purely RIGHT. You'd need to remove the TN activity on the
% UP channel, but you'd not be inducing any DOWN with the new target.
